\chapter{Introduction}
\label{ch:introduction}

\section{History}

The miniaturization and economical availability of technological systems has lead to their massive adoption
in agriculture. Armed with data from sensors and external sources such as local 
weather, farmers who implement precision agriculture are gaining deeper understanding of their operations.
This enables them to better manage key resources while increasing productivity. Furthermore machines 
today are capable of analyzing and storing large amounts of data which wasn't possible a few years ago. 
The benefits of precision agriculture can be already seen in greater cost savings and higher yield. 
Greater precision in farming has already proved its benefits. Focusing mostly on data collection, 
analysis, and visualization decision-making for the farmers can be greatly eased. This is now known 
as Smart Farming. Data-driven farming is on course to reshape the entire agricultural sector.

\section{Motivation}

Animals are naturally dynamic and their behavior is hard to predict. Caged or farm animals can 
be easily monitored within the confines of the facility. Their behavior and movement can be controlled. 
However in the case of free-range animals, where the animal is not confined and has access to the outdoors,
this is very difficult. In such a case the animal's behavior is hard to control and predict.

The farmer needs a system which can help in the decision making of the free-range farm.
Several RFID systems are installed on a free-range pig farm in Hungary to track the movement of pigs.
The main purpose is to collect information which data scientists can use to come up with models
which can provide useful information. 

The data scientists however need a robust system to deploy their models and put them into production.
This application fills the gap between the data scientist and the farmer. It needs to be flexible
as new data and new analysis can be developed by the scientists. It should also be simple
enough so that the farmer can use it without much technical knowledge.

\section{Introduction}

I am developing a Django web application for data collection and analysis in which a user can
upload several text files of data. The data is then stored and the analysis is automatically run in the
background. The results are stored and can be seen as visualizations. The gathered data can be browsed in the system.
The application is easily extendible and does not require a lot of development knowledge. There are pre-defined places where
any new feature can be plugged in and become ready to use in production. This will allow not only rapid prototyping
but also it will provide continuous feedback to the farmer about the work of the data scientists.

\section{Outline}

In Chapter \ref{ch:user}, we focus on how to use this web application from the users perspective. 
A user will upload new data files and the application will run the analysis on newly uploaded data.
It will then update the visualization with the results

Chapter \ref{ch:developer} discusses the details of this program.
The libraries and the models used in this project are explained. 
The architecture of the web application which makes it modular is explained in detail with an example.

The final chapter (Chapter \ref{ch:conclusion}) is the thesis conclusion 
which will sum everything and we will discuss further improvements and best practices